% James Pearson Hughes's Resume
% URL: https://github.com/xiongchiamiov/Resume
% Forked from Chris Gibson's resume
% URL: https://github.com/cgibson/Resume
% Which is in turn based on resume tex file by Kamil Wojcicki
% URL: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,line]{resume}

\usepackage{graphicx}
% Apparently this is needed for /text
\usepackage{amsmath}

\begin{document}

\name{\huge \sc{James\hspace{3.2mm}Pearson\hspace{1.5mm}Hughes}\vspace{2mm}}
{
    \hfill hireme@mail.changedmy.name       \vspace{0mm}\\\vspace{0mm}%
    \hfill https://github.com/xiongchiamiov \vspace{0mm}\\\vspace{-9mm}%
}

\begin{resume}

    \vspace{-3mm}
    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle \textbf{\large{S}\small{UMMARY}}}

    Former Site Reliability Engineer turned leader: the squishy human bits that
    use computers are fascinating, and org structures are the complex systems I
    focus on now.  Start with empathy, move to understanding the problems, and
    focus on solutions improve everyone's lives.
    \vspace{1.7mm}\\%
    I especially love working at companies that are undergoing the growth
    transition from ``Everything is great" to ``Why are there so many
    communication problems now?".

    \vspace{-1mm}

\sectionline
    %__________________________________________________________________________________________________________________
    % Leadership
    \section{\mysidestyle \textbf{\large{L}\small{EADERSHIP}}}

    % Loop Returns
    \text{\listing Loop Returns}
    \vspace{1mm}\\%
    \textbf{Staff Site Reliability Engineer} \hfill \textbf{January 2024 -- August 2024}\\
    As the first staff+ engineer outside of product engineering, began the
    process of defining a cohesive vision across the DevOps, DevEx, and
    Security teams.\\
    Established lines of communication across to product engineering, settling
    several major bubbling issues.\\
    Worked with a director to define the tech lead role, and mentored
    burgeoning tech leads both in a group setting as well as individually.

    \textit{Example of work:}  When I arrived, the main burden of technical
    leadership had been resting on the other two staff engineers (no principal
    engineer or CTO).  They had spent much time thoughtfully creating a
    technical vision for the company; the next struggle was in getting it
    implemented.\\
    Upon investigation, the primary breakdown was in translating down to the
    next level of the company hierarchy:  many of the TLs and EMs didn't know
    that translating this vision into actions for their team was their
    responsibility, and those that did largely struggled with prioritization
    and knowing \textit{how} to do this.  I pushed to restart a recurring
    meeting of technical leadership and change it from a round-robin recitation
    of what each team had done, and created a Slack channel as well for more
    off-the-cuff discussions. A recurring theme that appeared in those early
    meetings was ``Ok, but how are we supposed to actually do that?".\\
    Getting them talking to each other about this was an important step because
    it allowed them to trade ideas and spur each others' thought; long-term the
    goal was to have this be primarily self-sustaining.  In the meantime, I
    provided some targeted support to build momentum:
    \begin{enumerate}
        \item In group discussions, after giving space for others, giving
            advice on specific actions to prioritize projects (for instance,
            using Jira tagging and reports to keep track of manual work that
            could be eliminated through reduction of tech debt) - or sometimes
            just encouragement.
        \item For leads who requested it, being present in discussions to help
            provide backup as someone with a staff title.
        \item Every Friday, posting a link in the Slack channel to some bit of
            interesting leadership reading with how I had been thinking of
            applying it to my work, to remind folks to set aside time to step
            back from the onslaught of daily concerns.
    \end{enumerate}
    \vspace{-4mm}
    A director outside my reporting chain had been working on defining the tech
    lead role, and so I also joined with them to get that finished and
    repeatedly inserted into our discussions with tech leads.  My major
    contribution there was to genericize many of the concepts from applying
    only to product development and instead work also for my group (Platform),
    as well as the data engineering group (who didn't have a representative in
    the technical leadership groups).

    % Winnie
    \text{\listing Winnie}
    \vspace{1mm}\\%
    \textbf{Staff Site Reliability Engineer} \hfill \textbf{February 2022 -- January 2024}\\
    Role originator and owner of infrastructure, platform, pipeline, and security; defining vision and multi-year strategy and prioritizing backlog of tech debt.\\
    Reported to the VP Eng and worked across all teams to identify duplicate work, address architectural problems, and build a collaborative culture of learning and improvement.\\
    Member of eng managers meeting and substituted for a manager on parental leave.\\
    \textit{Key technologies:} AWS, Python, Pulumi, Github Actions

    % WePay
    \text{\listing WePay (acquired by JPMorgan Chase)}
    \vspace{1mm}\\%
    \textbf{Sr Staff Site Reliability Engineer} \hfill \textbf{May 2021 -- February 2022}\\
    Identified and addressed org-wide technology, process, and people problems. Recognized common origins of different problems and extracted them into strategic projects. Sponsored under-leveled engineers. Served at the pleasure of the Senior Director of DevOps.\\
    Owner of and interviewer trainer for SRE interview module.  Active member of hiring committee, making leveling and hiring decisions for all of engineering.\vspace{1mm}\\
    \textbf{Manager, Site Reliability Engineering} \hfill \textbf{March 2020 -- May 2021}\\
    Provided a first line of time defense for the team.  Worked with other engineering and product leads to plan and prioritize projects.\vspace{1mm}\\
    \textit{Key technologies:} GCP, Kubernetes, Ansible, Sensu

\pagebreak
\sectionline
    %__________________________________________________________________________________________________________________
    % Individual Contributor
    \section{\mysidestyle \textbf{\large{I}\small{NDIVIDUAL} \large{C}\small{ONTRIBUTOR}}}

    % WePay
    \text{\listing WePay (acquired by JPMorgan Chase)}
    \vspace{1mm}\\%
    \textbf{Senior Site Reliability Engineer} \hfill \textbf{February 2017 -- March 2020}\\
    Embedded within an application team to provide a close reliability partner.\\
    \textit{Key technologies:} GCP, Kubernetes, Ansible, Sensu

    % Zoox
    \text{\listing Zoox}
    \vspace{1mm}\\%
    \textbf{DevOps Engineer} \hfill \textbf{December 2015 -- February 2017}\\
    Introduced operations practices and tools into a rapidly growing autonomous vehicle company.
    Worked on a wide range of tasks, including web development (Flask, Pyramid, custom C++, custom Python), build systems (Bazel), an in-house deploy application, operations for several dozen applications, network security, AWS user support, software documentation, and organization-wide standards.

    % reddit
    \text{\listing reddit}
    \vspace{1mm}\\%
    \textbf{Software Engineer} \hfill \textbf{August 2014 -- December 2015}\\
    One of half a dozen engineers responsible for user-facing features on reddit.com, a site with over 200 million monthly active users.
    Fixed many bugs and annoyances that had been present for years.
    Built relationships with third-party add-on developers and community moderators.
    Implemented an A/B testing framework, a new comment sort and display algorithm, one of the most well-received features in site history (non-silent sidewide bans), and an expanded image preview system used by mobile web and third-party apps.
    Constantly refactored, documented, and added tests.
    Most work available for perusal at https://github.com/reddit-archive/reddit/commits?author=xiongchiamiov .

    % iFixit
    \text{\listing iFixit}
    \vspace{1mm}\\%
    \textbf{Web Operations Lead Engineer} \hfill \textbf{June 2012 -- August 2014}\\
    \textbf{DevOps Engineering Intern} \hfill \textbf{March 2011 -- June 2012}\\
    Implemented caching system that prevents previously-frequent media-induced downtimes.
    Implemented and championed application monitoring, leading to improvements in performance, stability, and user experience.
    Wrote alerting system that gives developers direct access to failure reports.
    Kickstarted thriving internal high-level documentation project.
    Improved startup time of application servers from 15 minutes with 25\% failures to \textless5 minutes with no failures.

    % XYZ Textbooks
    \text{\listing XYZ Textbooks} \vspace{1mm}\\%
    \textbf{Web Programmer / Sysadmin} \hfill \textbf{June 2008 -- March 2011}

    % Cal Poly
    \text{\listing Cal Poly} \vspace{1mm}\\%
    \textbf{Web Developer} \hfill \textbf{July 2008 -- November 2008}

\sectionline
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing California Polytechnic University}, San Luis Obispo, California \vspace{1mm}\\
    \textsl{B.S of Software Engineering} \vspace{-3mm}\\\vspace{-1mm}%

\sectionline
    %__________________________________________________________________________________________________________________
    % Skills / Keywords
    \section{\mysidestyle \textbf{\large{S}\small{KILLS} / \large{K}\small{EYWORDS}}}

    \textbf{Cloud Computing:} Amazon Web Services (AWS), Google Cloud Platform (GCP)\\
    \textbf{Containers:} Kubernetes, Docker Desktop/Compose, Amazon ECS\\
    \textbf{Infrastructure as Code:} Ansible, Pulumi\\
    \textbf{CI/CD:} Github Actions, Teamcity, Jenkins\\
    \textbf{Linux:} Red Hat family (CentOS), Arch Linux, Debian family (Ubuntu, Debian)\\
    \textbf{Monitoring/Alerting:} Sensu, Graphite, StatsD, pipe-to-graphite, collectd\\
    \textbf{Scripting:} Bash and utils (sed, awk, grep), Python, Ruby\\
    \textbf{Backend:} Python (Django, Flask, Pyramid), PHP (Symfony, custom), Ruby (Sinatra)\\
    \textbf{Databases:} MySQL, Redis, PostgreSQL, SQLite, DynamoDB, Cassandra\\
    \textbf{Web Application servers/proxies:} Varnish, Apache, HAProxy, Nginx, Tomcat, uWSGI\\
    \textbf{Version control systems:} Git, Mercurial, Subversion\\
    \textbf{Queueing/Messaging:} Gearman, Kafka, RabbitMQ, beanstalkd

\end{resume}
\end{document}
